Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-15 paper/section_4_datasets.tex
Move entity distribution to appendix

\begin{figure}[t]
   \begin{center}
   \includegraphics[width=0.99\linewidth]{figures/figure_2_entities.pdf}
   \end{center}
      \caption{Entity distribution in NYTimes800k training captions. The four
               most common entity types are personal names, geopolitical
               entities, organizations, and dates.}
   \label{fig:entities}
\end{figure}

@@

Entities play an important role in the dataset, with 97\% of captions
containing at least one named entity. As shown in Figure~\ref{fig:entities},
the most popular entity type are names of people, comprising a third of all
named entities. Furthermore, 71\% of training images contain at least one face
and 68\% of training captions mention at least one persons name. Figure
\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
personal names. One important observation is that the majority of captions
contain at most four names.

>>>>

@@

Entities play an important role in the dataset, with 97\% of captions
containing at least one named entity.
The most popular entity type are names of people, comprising a third of all
named entities (see the supplementary material for a detailed breakdown of entity types). Furthermore, 71\% of training images contain at least one face
and 68\% of training captions mention at least one persons name. Figure
\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
personal names. One important observation is that the majority of captions
contain at most four names.
